Brief Article

### 2021-08-19 Draft.tex
added 5 moer references

@@

>>>>

User evaluation methods and the impact of think-aloud on user testing \cite{mcdonald2020impact, ericsson1984protocol, fox2011procedures}.

Task analysis of the challenges of shell programming \cite{gandhi2020lightening}.

Optimizing visual and textual information presented on search user interfaces \cite{treharne2012optimising}.

@@

\section{Discussion}
